---
title: "M4Q2 Missing Data"
author: "Taylor Rogers"
date: '2022-06-09'
output: html_document
---

```{r}
#install.packages("mice")

library(tidyverse)
library(VIM)
library(mice)
```

```{r}
grades = read.csv("class-grades.csv")
```

```{r}
str(grades)
summary(grades)
```

##Question 1: Tutorial, Midterm, TakeHome, and Final

```{r}
vim_plot = aggr(grades, numbers = TRUE, prop = c(TRUE, FALSE),cex.axis=.7)
```

## Question 2: Yes, there are student with more than one piece of data missing

```{r}
grades_rowdel = grades %>% drop_na() 
```

## Question 3: 89 rows remain

```{r}
grades_coldel = grades %>% select(-Tutorial, -Midterm, -TakeHome, -Final) 
```

##Question 4: 2 columns remain

##Question 5: Row-wise deletion seems more appropriate for this data set, since at least one student missed each of the assignments. There is no data left to analyze when column-wise deletion is used. 

```{r}
set.seed(123) #sets seed for random number generator
imp_grades = mice(grades, m=5, method='pmm', printFlag=FALSE)
#m is the number of imputations, 5 is a reasonable value as a default
#pmm is "predictive mean matching" = imputation method for numeric data
#printFlag reduces amount of output
summary(imp_grades)
```

```{r}
grades_complete = complete(imp_grades)
```

```{r}
mean(grades_complete$Final)
```


##Question 6: 68.33
